\documentclass{ximera}
\title{Factor Coefficients Method Practice 1}



\begin{document}
\input{Useful-Sage-Macros}

\begin{sagesilent}
def RandInt(a,b):
    """ Returns a random integer in [`a`,`b`]. Note that `a` and `b` should be integers themselves to avoid unexpected behavior.
    """
    return QQ(randint(int(a),int(b)))
    # return choice(range(a,b+1))

def NonZeroInt(b,c, avoid = [0]):
    """ Returns a random integer in [`b`,`c`] which is not in `av`. 
        If `av` is not specified, defaults to a non-zero integer.
    """
    while True:
        a = RandInt(b,c)
        if a not in avoid:
            return a

def cpx(z):
    if z == 0:
        return LatexExpr('0')
    a = z.real()
    b = z.imag()
    if (a == 0) or (b==0) :
        return LatexExpr(latex(z))
    elif b > 0:
      s = '+'
    else:
      s = '-'
    return latex(a) + LatexExpr(s) + latex(abs(b) * i)



### Problem p1
p1c1 = RandInt(-5,5)
p1c2 = RandInt(-5,5)
p1c3 = RandInt(-5,5)
p1c4 = NonZeroInt(-5,5)

p1complex1 = p1c1 + p1c2*i
p1complex2 = p1c3 + p1c4*i

p1complex1d = cpx(p1c1 + p1c2*i)
p1complex2d = cpx(p1c3 + p1c4*i)

p1ans1 = (p1complex1/p1complex2).real()
p1ans2 = (p1complex1/p1complex2).imag()

p1h1 = cpx(p1complex2.conjugate())



### Problem p2
p2c1 = RandInt(-5,5)
p2c2 = RandInt(-5,5)
p2c3 = RandInt(-5,5)
p2c4 = NonZeroInt(-5,5)

p2complex1 = p2c1 + p2c2*i
p2complex2 = p2c3 + p2c4*i

p2complex1d = cpx(p2c1 + p2c2*i)
p2complex2d = cpx(p2c3 + p2c4*i)

p2ans1 = (p2complex1/p2complex2).real()
p2ans2 = (p2complex1/p2complex2).imag()

p2h1 = cpx(p2complex2.conjugate())


### Problem p3
p3c1 = RandInt(-5,5)
p3c2 = RandInt(-5,5)
p3c3 = RandInt(-5,5)
p3c4 = NonZeroInt(-5,5)

p3complex1 = p3c1 + p3c2*i
p3complex2 = p3c3 + p3c4*i

p3complex1d = cpx(p3c1 + p3c2*i)
p3complex2d = cpx(p3c3 + p3c4*i)

p3ans1 = (p3complex1/p3complex2).real()
p3ans2 = (p3complex1/p3complex2).imag()

p3h1 = cpx(p3complex2.conjugate())


### Problem p4
p4c1 = RandInt(-5,5)
p4c2 = RandInt(-5,5)
p4c3 = RandInt(-5,5)
p4c4 = NonZeroInt(-5,5)

p4complex1 = p4c1 + p4c2*i
p4complex2 = p4c3 + p4c4*i

p4complex1d = cpx(p4c1 + p4c2*i)
p4complex2d = cpx(p4c3 + p4c4*i)

p4ans1 = (p4complex1/p4complex2).real()
p4ans2 = (p4complex1/p4complex2).imag()

p4h1 = cpx(p4complex2.conjugate())




\end{sagesilent}


\begin{problem}
    Simplify the following complex expression into standard form.
    \[
        \frac{\sage{p1complex1d}}{\sage{p1complex2d}} = \answer{\sage{p1ans1}} + \answer{\sage{p1ans2}}\cdot i
    \]
    \begin{feedback}
        Remember to multiply the top and bottom of the fraction by the conjugate of the bottom; i.e. $\sage{p1h1}$ and foil out. This should get you a real denominator.
        
        Also notice that the ``$i$'' is already provided, so you don't need to type into your answer.
    \end{feedback}
    
\end{problem}


\begin{problem}
    Simplify the following complex expression into standard form.
    \[
        \frac{\sage{p2complex1d}}{\sage{p2complex2d}} = \answer{\sage{p2ans1}} + \answer{\sage{p2ans2}}\cdot i
    \]
    \begin{feedback}
        Remember to multiply the top and bottom of the fraction by the conjugate of the bottom; i.e. $\sage{p2h1}$ and foil out. This should get you a real denominator.
        
        Also notice that the ``$i$'' is already provided, so you don't need to type into your answer.
    \end{feedback}
    
\end{problem}


\begin{problem}
    Simplify the following complex expression into standard form.
    \[
        \frac{\sage{p3complex1d}}{\sage{p3complex2d}} = \answer{\sage{p3ans1}} + \answer{\sage{p3ans2}}\cdot i
    \]
    \begin{feedback}
        Remember to multiply the top and bottom of the fraction by the conjugate of the bottom; i.e. $\sage{p3h1}$ and foil out. This should get you a real denominator.
        
        Also notice that the ``$i$'' is already provided, so you don't need to type into your answer.
    \end{feedback}
    
\end{problem}


\begin{problem}
    Simplify the following complex expression into standard form.
    \[
        \frac{\sage{p4complex1d}}{\sage{p4complex2d}} = \answer{\sage{p4ans1}} + \answer{\sage{p4ans2}}\cdot i
    \]
    \begin{feedback}
        Remember to multiply the top and bottom of the fraction by the conjugate of the bottom; i.e. $\sage{p4h1}$ and foil out. This should get you a real denominator.
        
        Also notice that the ``$i$'' is already provided, so you don't need to type into your answer.
    \end{feedback}
    
\end{problem}



\end{document}