\documentclass{ximera}

\title{Goals of this Course}
\begin{document}
\begin{abstract}
This course has several concurrent but different goals.
\end{abstract}
\maketitle

Watch the video on this section below!

\youtube{-x5-LinK1LY}

Simply put, the goal of this course is to prepare one for Survey of Calculus (MAC2233) or, in conjunction with a trigonometry class (MAC1114), for Analytic Geometry and Calculous One (MAC2311). \\

More conceptually however, the real goal of this course is to teach how to problem solve and use mathematical reasoning in an industrial or professional setting. Often the process of modeling and reasoning are devalued or even sacrificed entirely in an effort to teach the mechanical skills of arithmetic. This is typically met with exasperation and confusion by students who ask "What's the point of learning this?", which is a valid question in any classroom. Unfortunately the point of learning mathematics is not the computation aspect, but the reasoning and modelings aspects... those very things that are often pushed out in an effort to improve the more easily assessed computational skills. So, a more simply put, if far less simple, answer, is "The goal of this course is to teach you to 'think'." 


\begin{problem}
    What course should you take if you want to take the ``classic'' calculus one course (Analytic Geometry and Calculus One)?
    \begin{multipleChoice}
        \choice{MAC2311}
        \choice{MAC2234}
        \choice{MAC2312}
        \choice{MAC2313}
        \choice[correct]{MAC1114}
        \choice{MAC2233}
    \end{multipleChoice}
\end{problem}

\begin{problem}
    What course should you take if you want to take the followup calculus course to this (MAC1140) course? 
    \begin{multipleChoice}
        \choice{MAC2311}
        \choice{MAC2234}
        \choice{MAC2312}
        \choice{MAC2313}
        \choice{MAC1114}
        \choice[correct]{MAC2233}
    \end{multipleChoice}
\end{problem}

\begin{problem}
    Who should you talk to about changing courses or otherwise deciding on the best courses to take to graduate on time and get the mathematics courses you both need and want? (Select all that apply)
    \begin{selectAll}
        \choice{You Instructor for this course (MAC1140)}
        \choice{Any math instructor}
        \choice[correct]{The undergraduate coordinator/advisor in the math department}
        \choice[correct]{Your academic advisor}
        \choice{Your parents}
        \choice{Your peers}
    \end{selectAll}
\end{problem}


\end{document}