\documentclass{ximera}

\title{Terminology To Know}
\begin{document}
\begin{abstract}
    These are important terms and notations for this section.
\end{abstract}
\maketitle

\subsection*{Terminology}
\begin{definition}[Monomial]
    A term of the form $ax^n$ for some constant $a$ and some non-negative integer $n$. From ``mono" meaning ``one" and ``nomen" meaning ``name".
\end{definition} 

\begin{definition}[Binomial]
    An expression that is the sum or difference of two monomials. From "bi" meaning ``two".
\end{definition} 

 \begin{definition}[Polynomial]
    A function or expression that is entirely composed of the sum or differences of monomials. From ``poly" meaning ``many".
\end{definition} 

\begin{definition}[Leading Term (of a polynomial)]
    The \textit{leading term} of a polynomial is the term with the largest exponent, along with its coefficient. Another way to describe it (which is where this term gets its name) is that; if we arrange the polynomial from highest to lowest power, than the first term is the so-called `leading term'.\\
    \textbf{For Example:} For the polynomial $p(x) = x^2 - 13x^3 + 4x - 1$ we could rewrite it in descending order of exponents, to get $p(x) = -13x^3 + x^2 + 4x - 1$ which makes clear that $-13x^3$ as the `leading term' of $p(x)$.
\end{definition} 

\begin{definition}[(Complex) Conjugates]
    A pair of complex numbers whose real parts are the same, and whose imaginary parts differ only by a negative sign are called complex conjugates. \\
    \textbf{Note:} We often ask for `the complex conjugate to' a complex number, in which case we are asking for the associated number in the pair. \\
    \textbf{For Example:} The numbers $5 + 3i$ and $5 - 3i$ are complex conjugates. If one were to ask `what is the complex conjugate of $5 - 3i$ the answer would be the other number of the complex conjugate pair, ie $5 + 3i$.
\end{definition} 

\begin{definition}[Curvature]
    Curvature refers to monotonicity (increasing/decreasing) and the concavity (bending up or down) of a curve.
\end{definition} 

\begin{definition}[Irreducible Polynomial]
    A polynomial that cannot be factored any further. We will often specify under what type of numbers we are factoring the polynomial; eg real numbers or complex numbers. This indicates whether all numbers in the factored form must be real or complex numbers (respectively).\\
    \textbf{For Example:} $(x^2+1)$ is \textit{irreducible under the real numbers} because there is no way to factor this quadratic with real numbers only. \textbf{However} $x^2+1$ is \textit{not} irreducible under the complex numbers, as we can write $x^2+1 = (x+i)(x-i)$.
\end{definition} 

\begin{definition}[Root (of a polynomial)]
    A root of a polynomial is an irreducible polynomial that is a factor of the given polynomial.\\
    \textbf{For Example:} The polynomial $x + 1$ is a root of the polynomial $x^2 - 1$ because $(x+1)(x-1) = x^2 -1$. In comparison $x^2-1$ is \textit{not} a root of the polynomial $x^4-1$, even though $(x^2-1)(x^2+1) = x^4-1$ because $x^2-1$ is \textit{not} irreducible.
\end{definition}

\begin{definition}[Multiplicity (of a value/zero)]
    The multiplicity of a value is a count of how many times that value occurs. This is most often used in reference to the `multiplicity of a zero' or `multiplicity of a root'. \\
    \textbf{For Example:} Let's say we have factored a polynomial into the form:
    \[
        p(x) = (x+1)^3(x-1)^2(x+5)(x+17)
    \]
    We would say that ``the root $(x+1)$ has multiplicity 3'', because the term $(x+1)$ occurs 3 times (hence the power of 3). Similarly the root $(x-1)$ has multiplicity 2, and the roots $(x+5)$ and $(x+17)$ both have multiplicity 1. This can be even easier to see if we re-write $p(x)$ without using exponents;
    \[
        p(x) = (x+1)(x+1)(x+1)\cdot(x-1)(x-1)\cdot(x+5)(x+17)
    \]
    \textbf{NOTE:} When we say that a polynomial has $n$ roots ``up to multiplicity" what we mean is that if we add all the multiplicity numbers together of all the roots, we would get $n$. So in the case of $p(x)$ we would say $p(x)$ has 7 roots ``up to multiplicity" since there are 4 \textit{unique} ``roots", but two of them occur more than once, so there are a total of 7 roots if you account for repeats.
\end{definition}

\subsection*{Notation}
\begin{definition}[Notation for an arbitrary polynomial]
    The standard notation for a polynomial ($p(x)$) of degree $n$ and with coefficients $c_0, c_1, \dots , c_n \in \mathbb{R}$ is as follows:
    \[
        p(x) = c_nx^n + x_{n-1}x^{n-1} + c_{n-2}x^{n-2} + \dots + c_2x^2 + c_1x + c_0
    \]
    This notation should be explained however. The polynomial $p(x)$, is degree $n$, so its highest power is $n$, and each of the coefficients ``$\in\mathbb{R}$'' means that all the coefficients are real numbers. The fact that there are $c_0, c_1, \dots c_n$ and the polynomial is degree $n$ is not a coincidence; the subscript on the coefficient and the degree of the polynomial are the same $n$. Moreover, looking at the definition of $p(x)$ above you can see that each term is of the form 
    \[
        c_{\text{(some value)}} x^{\text{(the same value)}}
    \]
    meaning that the power of $x$ and the subscript on the coefficient match. This is also not an accident, this is how we tell which coefficient goes with which term. For example; if we wanted to know the coefficient of $x^{17}$, we would immediately know that is $c_{17}$ because that's how they are named.
    
    Finally, notice that the last term in the standard notation is just $c_0$, however, that is better written as $c_0x^0$, meaning that it conforms to all the other terms. It's just easier to simplify the $x^0 = 1$ and then omit writing it, so we only write $c_0$. But notice that the pattern holds for every term, including the last one, despite the fact that we don't write the $x^0$ piece of the last term.
\end{definition}

\end{document}